---
title: "Comparison of South and NorthTyrol"
author: "fabian gruber"
date: "02/14/2017"
output: html_document
---

 Due to the surprisingly poor model results of topographic position in South Tyrol, a comparable dataset from North Tyrol was acquired. Due to computational time the procedure was performed for only one automated classification algorithm as well as the terrain parameter - based approach. Due to its relatively good performance and it haveing less parameters than Schmidts fuzzy elements, the r.geomorphon - based landform classification was chosen to represenet the various classes of automated landform classifications.

```{r}
source("/home/fabs/Data/paper1_lenny/fabians_and_rossiters_functions.R")
```

##Macro scale GL1
### Geomorphons - UA

```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/results_selection/svm_fw_10fold_3p_Def_red_mak_allgeoms//",kk = 1:10,endround = 3,yrange = c(0.45,0.6),geheim = "geheimerprederror",error="prederror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_UA_5p_Def_red_mak_geomcols/",kk = 1:10,endround = 5,yrange = c(0.45,0.6),geheim = "geheimerprederror",error="prederror")
```

### Terrain parameters- UA
```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/results_selection/svm_fw_10fold_10p_Def_red_mak_allterrain",kk = 1:10,endround = 10,yrange = c(0.45,0.6),geheim = "geheimerprederror",error="prederror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_UA_5p_Def_red_mak_terraincols/",kk = 1:10,endround = 5,yrange = c(0.45,0.6),geheim = "geheimerprederror",error="prederror")
```


##Meso scale GL1
### Geomorphons- UA

```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/results_selection/svm_fw_10fold_3p_Def_red_mes_allgeoms//",kk = 1:10,endround = 3,yrange = c(0.45,0.7),geheim = "geheimerprederror",error="prederror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_UA_5p_Def_red_mes_geomcols/",kk = 1:10,endround = 5,yrange = c(0.45,0.7),geheim = "geheimerprederror",error="prederror")
```

### Terrain parameters- UA
```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/results_selection/svm_fw_10fold_10p_Def_red_mes_allterrain",kk = 1:10,endround = 10,yrange = c(0.4,0.65),geheim = "geheimerprederror",error="prederror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_UA_5p_Def_red_mes_terraincols/",kk = 1:10,endround = 5,yrange = c(0.4,0.65),geheim = "geheimerprederror",error="prederror")
```


##Macro scale GL2
### Geomorphons- UA

```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/results_selection/svm_fw_10fold_3p_EZ_class_allgeoms//",kk = 1:10,endround = 3,yrange = c(0.4,0.55),geheim = "geheimerprederror",error="prederror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_UA_5p_EZ_class_geomcols/",kk = 1:10,endround = 5,yrange = c(0.4,0.55),geheim = "geheimerprederror",error="prederror")
```

### Terrain parameters- UA
```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/results_selection/svm_fw_10fold_10p_EZ_class_allterrain/",kk = 1:10,endround = 10,yrange = c(0.4,0.55),geheim = "geheimerprederror",error="prederror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_UA_5p_EZ_class_terraincols//",kk = 1:10,endround = 5,yrange = c(0.4,0.55),geheim = "geheimerprederror",error="prederror")
```

##Meso scale GL2
### Geomorphons- UA

```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/results_selection/svm_fw_10fold_3p_EZ_class_mes_allgeoms//",kk = 1:10,endround = 3,yrange = c(0.3,0.50),geheim = "geheimerprederror",error="prederror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_UA_5p_EZ_class_mes_geomcols/",kk = 1:10,endround = 5,yrange = c(0.3,0.50),geheim = "geheimerprederror",error="prederror")
```

### Terrain parameters- UA
```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/results_selection/svm_fw_10fold_10p_EZ_class_mes_allterrain/",kk = 1:10,endround = 10,yrange = c(0.3,0.45),geheim = "geheimerprederror",error="prederror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_UA_5p_EZ_class_mes_terraincols//",kk = 1:10,endround = 5,yrange = c(0.3,0.45),geheim = "geheimerprederror",error="prederror")
```

#How about quality?
##Macro scale GL1
### Geomorphons- Q

```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/quality_svm_fw_10fold_2pDef_red_mak_allgeoms/",kk = 1:10,endround = 2,yrange = c(0.75,0.85),geheim = "cv_quality",error="cv_qualityerror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_quality_5p_Def_red_mak_geomcols/",kk = 1:10,endround = 2,yrange = c(0.75,0.95),geheim = "cv_quality",error="cv_qualityerror")
```

### Terrain parameters- Q
```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/quality_svm_fw_10fold_2pDef_red_mak_tpiterraintophat/",kk = 1:10,endround = 2,yrange = c(0.75,0.95),geheim = "cv_quality",error="cv_qualityerror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_quality_5p_Def_red_mak_terraincols/",kk = 1:10,endround = 2,yrange = c(0.75,0.95),geheim = "cv_quality",error="cv_qualityerror")
```


##Meso scale GL1
### Geomorphons- Q

```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/quality_svm_fw_10fold_2pDef_red_mes_allgeoms/",kk = 1:10,endround = 2,yrange = c(0.80,0.95),geheim = "cv_quality",error="cv_qualityerror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_quality_5p_Def_red_mes_geomcols//",kk = 1:10,endround = 2,yrange = c(0.80,0.95),geheim = "cv_quality",error="cv_qualityerror")
```

### Terrain parameters- Q 
```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/quality_svm_fw_10fold_6pDef_red_mes_tpiterraintophat/",kk = 1:10,endround = 6,yrange = c(0.75,0.90),geheim = "cv_quality",error="cv_qualityerror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_quality_5p_Def_red_mes_terraincols/",kk = 1:10,endround = 2,yrange = c(0.75,0.9),geheim = "cv_quality",error="cv_qualityerror")
```


##Macro scale GL2
### Geomorphons- Q

```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/quality_svm_fw_10fold_2pEZ_class_allgeoms//",kk = 1:10,endround = 2,yrange = c(0.55,0.75),geheim = "cv_quality",error="cv_qualityerror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_quality_5p_EZ_class_geomcols/",kk = 1:10,endround = 5,yrange = c(0.55,0.75),geheim = "cv_quality",error="cv_qualityerror")
```

### Terrain parameters- Q
```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/quality_svm_fw_10fold_2pEZ_class_alltpilandforms/",kk = 1:10,endround = 2,yrange = c(0.55,0.75),geheim = "cv_quality",error="cv_qualityerror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_quality_5p_EZ_class_terraincols//",kk = 1:10,endround = 5,yrange = c(0.55,0.75),geheim = "cv_quality",error="cv_qualityerror")
```

##Meso scale GL2
### Geomorphons- Q

```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/quality_svm_fw_10fold_2pEZ_class_mes_allgeoms/",kk = 1:10,endround = 2,yrange = c(0.55,0.65),geheim = "cv_quality",error="cv_qualityerror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_quality_5p_EZ_class_mes_geomcols/",kk = 1:10,endround = 5,yrange = c(0.55,0.65),geheim = "cv_quality",error="cv_qualityerror")
```

### Terrain parameters- Q
```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/quality_svm_fw_10fold_2pEZ_class_mes_tpiterraintophat/",kk = 1:10,endround = 2,yrange = c(0.3,0.70),geheim = "cv_quality",error="cv_qualityerror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_quality_5p_EZ_class_mes_terraincols//",kk = 1:10,endround = 5,yrange = c(0.3,0.7),geheim = "cv_quality",error="cv_qualityerror")
```
