---
title: "Comparison of South and NorthTyrol"
author: "fabian gruber"
date: "02/14/2017"
output: html_document
---

 Due to the surprisingly poor model results of topographic position in South Tyrol, a comparable dataset from North Tyrol was acquired. Due to computational time the procedure was performed for only one automated classification algorithm as well as the terrain parameter - based approach. Due to its relatively good performance and it haveing less parameters than Schmidts fuzzy elements, the r.geomorphon - based landform classification was chosen to represenet the various classes of automated landform classifications.

```{r}
source("/home/fabs/Data/paper1_lenny/fabians_and_rossiters_functions.R")
load("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/relieflegends.RData")
load("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/mesomakrolegends.RData")
load("/home/fabs/Data/paper1_lenny/modeldata_SuedundNordtirol.RData")
```

##Macro scale GL1
### Geomorphons - UA

```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/results_selection/svm_fw_10fold_3p_Def_red_mak_allgeoms//",kk = 1:10,endround = 3,yrange = c(0.45,0.6),geheim = "geheimerprederror",error="prederror")
predict_radial_newlegend_full(modeldata=ST_makrored,dependent = "Def_red_mak",predictors =  "geom_DTM_50m_avg_fl10_L400m",legend = makrolegend_gen1,doreturn=F)
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_UA_5p_Def_red_mak_geomcols/",kk = 1:10,endround = 5,yrange = c(0.45,0.6),geheim = "geheimerprederror",error="prederror")
predict_radial_newlegend_full(modeldata=NT_makrored,dependent = "Def_red_mak",predictors =  "geom_NT_50m_avg_L300m_10deg",legend = makrolegend_gen1,doreturn=F)

```

### Terrain parameters- UA
```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/results_selection/svm_fw_10fold_10p_Def_red_mak_allterrain",kk = 1:10,endround = 10,yrange = c(0.45,0.6),geheim = "geheimerprederror",error="prederror")
predict_radial_newlegend_full(modeldata=ST_makrored,dependent = "Def_red_mak",predictors = c("Topographic_Wetness_Index","profc_DTM_50m_avg_ws7","minic_DTM_50m_avg_ws5","slope_ws15"),legend = makrolegend_gen1,doreturn=F)
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_UA_5p_Def_red_mak_terraincols/",kk = 1:10,endround = 5,yrange = c(0.45,0.6),geheim = "geheimerprederror",error="prederror")
predict_radial_newlegend_full_naomit(modeldata=NT_makrored,dependent = "Def_red_mak",predictors =c("TPI_i0m_o200m_10m","slope_NT_50m_avg_ws350m","Longitudinal_Curvature_50m","minic_NT_ws250m"),legend = makrolegend_gen1,doreturn=F)
```


##Meso scale GL1
### Geomorphons- UA

```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/results_selection/svm_fw_10fold_3p_Def_red_mes_allgeoms//",kk = 1:10,endround = 3,yrange = c(0.45,0.7),geheim = "geheimerprederror",error="prederror")
predict_radial_newlegend_full(modeldata=ST_mesored,dependent = "Def_red_mes",predictors =  "geom_10m_fl8_L8",legend = ,mesolegend_gen1,doreturn=F)
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_UA_5p_Def_red_mes_geomcols/",kk = 1:10,endround = 5,yrange = c(0.45,0.7),geheim = "geheimerprederror",error="prederror")
predict_radial_newlegend_full_naomit(modeldata=NT_mesored,dependent = "Def_red_mes",predictors =  "geom_NT_L80m_8deg",legend =mesolegend_gen1,doreturn=F)
```

### Terrain parameters- UA
```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/results_selection/svm_fw_10fold_10p_Def_red_mes_tpiterrain/",kk = 1:10,endround = 10,yrange = c(0.4,0.65),geheim = "geheimerprederror",error="prederror")
predict_radial_newlegend_full(modeldata=ST_mesored,dependent = "Def_red_mes",predictors = c("TPI_i0m_o70m_10m","slope_DTM_50m_avg_ws3") ,legend = ,mesolegend_gen1,doreturn=F)
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/results_selection/svm_fw_10fold_10p_Def_red_mes_allterrain/",kk = 1:10,endround = 10,yrange = c(0.4,0.65),geheim = "geheimerprederror",error="prederror")
print("NORTH TYROL")
predict_radial_newlegend_full(modeldata=ST_mesored,dependent = "Def_red_mes",predictors =c("crosc_ws5","minic_ws15","slope_DTM_50m_avg_ws3","maxic_ws5"),legend = ,mesolegend_gen1,doreturn=F)
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_UA_5p_Def_red_mes_terraincols/",kk = 1:10,endround = 5,yrange = c(0.4,0.65),geheim = "geheimerprederror",error="prederror")
predict_radial_newlegend_full_naomit(modeldata=NT_mesored,dependent = "Def_red_mes",predictors =  c("TPI_i0m_o100m_10m","slope_NT_ws30m","crosc_NT_ws70m"),legend =mesolegend_gen1,doreturn=F)
```


##Macro scale GL2
### Geomorphons- UA

```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/results_selection/svm_fw_10fold_3p_EZ_class_allgeoms//",kk = 1:10,endround = 3,yrange = c(0.4,0.55),geheim = "geheimerprederror",error="prederror")
predict_radial_newlegend_full(modeldata=ST_ezclass,dependent = "EZ_class",predictors =  "geom_DTM_50m_avg_fl10_L400m",legend = makrolegend_gen2,doreturn=F)

print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_UA_5p_EZ_class_geomcols/",kk = 1:10,endround = 5,yrange = c(0.4,0.55),geheim = "geheimerprederror",error="prederror")
predict_radial_newlegend_full(modeldata=NT_ezclass,dependent = "EZ_class",predictors ="geom_NT_50m_avg_L800m_10deg",legend = makrolegend_gen2,doreturn=F)

```

### Terrain parameters- UA
```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/results_selection/svm_fw_10fold_10p_EZ_class_tpiterrain//",kk = 1:10,endround = 10,yrange = c(0.4,0.55),geheim = "geheimerprederror",error="prederror")
predict_radial_newlegend_full(modeldata=ST_ezclass,dependent = "EZ_class",predictors =  c("Topographic_Wetness_Index","profc_DTM_50m_avg_ws7","minic_DTM_50m_avg_ws5","slope_DTM_50m_avg_ws7"),legend = makrolegend_gen2,doreturn=F)

print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_UA_5p_EZ_class_terraincols//",kk = 1:10,endround = 5,yrange = c(0.4,0.55),geheim = "geheimerprederror",error="prederror")
predict_radial_newlegend_full_naomit(modeldata=NT_ezclass,dependent = "EZ_class",predictors =c("TPI_i0m_o200m_10m","profc_NT_50m_avg_ws750m","slope_NT_50m_avg_ws750m"),legend = makrolegend_gen2,doreturn=F)

```

##Meso scale GL2
### Geomorphons- UA

```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/results_selection/svm_fw_10fold_3p_EZ_class_mes_allgeoms//",kk = 1:10,endround = 3,yrange = c(0.3,0.50),geheim = "geheimerprederror",error="prederror")
predict_radial_newlegend_full(modeldata=ST_ezclassmes,dependent = "EZ_class_mes",predictors =  "geom_10m_fl8_L15",legend = mesolegend_gen2,doreturn=F)

print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_UA_5p_EZ_class_mes_geomcols/",kk = 1:10,endround = 5,yrange = c(0.3,0.50),geheim = "geheimerprederror",error="prederror")
predict_radial_newlegend_full_naomit(modeldata=NT_ezclassmes,dependent = "EZ_class_mes",predictors ="geom_NT_L500m_8deg",legend = mesolegend_gen2,doreturn=F)

```

### Terrain parameters- UA
```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/results_selection/svm_fw_10fold_10p_EZ_class_mes_tpiterrain//",kk = 1:10,endround = 10,yrange = c(0.3,0.45),geheim = "geheimerprederror",error="por")
predict_radial_newlegend_full(modeldata=ST_ezclassmes,dependent = "EZ_class_mes",predictors =  c("TPI_i0m_o90m_10m","Slope","Standardized_Height","maxic_ws7"),legend = mesolegend_gen2,doreturn=F)
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_UA_5p_EZ_class_mes_terraincols//",kk = 1:10,endround = 5,yrange = c(0.3,0.45),geheim = "geheimerprederror",error="prederror")
predict_radial_newlegend_full_naomit(modeldata=NT_ezclassmes,dependent = "EZ_class_mes",predictors =c("TPI_i50m_o100m_10m","Slope_degree_10m"),legend = mesolegend_gen2,doreturn=F)

```

#How about quality?
##Macro scale GL1
### Geomorphons- Q

```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/quality_svm_fw_10fold_2pDef_red_mak_allgeoms/",kk = 1:10,endround = 2,yrange = c(0.75,0.85),geheim = "cv_quality",error="cv_qualityerror")
predict_radial_newlegend_full(modeldata=ST_makrored,dependent = "Def_red_mak",predictors =  "geom_DTM_50m_avg_fl8_L400m",legend = makrolegend_gen1,doreturn=F)

print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_quality_5p_Def_red_mak_geomcols/",kk = 1:10,endround = 5,yrange = c(0.75,0.95),geheim = "cv_quality",error="cv_qualityerror")
predict_radial_newlegend_full(modeldata=NT_makrored,dependent = "Def_red_mak",predictors =  "geom_NT_50m_avg_L300m_10deg",legend = makrolegend_gen1,doreturn=F)

```

### Terrain parameters- Q
```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/quality_svm_fw_10fold_2pDef_red_mak_tpiterraintophat/",kk = 1:10,endround = 2,yrange = c(0.75,0.95),geheim = "cv_quality",error="cv_qualityerror")
#predict_radial_newlegend_full(modeldata=ST_makrored,dependent = "Def_red_mak",predictors =  ,legend = makrolegend_gen1,doreturn=F)

print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_quality_5p_Def_red_mak_terraincols/",kk = 1:10,endround = 5,yrange = c(0.75,0.95),geheim = "cv_quality",error="cv_qualityerror")
predict_radial_newlegend_full_naomit(modeldata=NT_makrored,dependent = "Def_red_mak",predictors = c("Topographic_Wetness_Index_50m","slope_NT_ws70m","profc_NT_50m_avg_ws750m","crosc_NT_50m_avg_ws450m") ,legend = makrolegend_gen1,doreturn=F)

```


##Meso scale GL1
### Geomorphons- Q

```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/quality_svm_fw_10fold_5pDef_red_mes_allgeoms/",kk = 1:10,endround = 5,yrange = c(0.80,0.95),geheim = "cv_quality",error="cv_qualityerror")
predict_radial_newlegend_full(modeldata=ST_mesored,dependent = "Def_red_mes",predictors =  "geom_10m_fl10_L15",legend = ,mesolegend_gen1,doreturn=F)

print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_quality_5p_Def_red_mes_geomcols//",kk = 1:10,endround = 5,yrange = c(0.80,0.95),geheim = "cv_quality",error="cv_qualityerror")
predict_radial_newlegend_full_naomit(modeldata=NT_mesored,dependent = "Def_red_mes",predictors =  "geom_NT_L120m_10deg",legend =mesolegend_gen1,doreturn=F)

```

### Terrain parameters- Q 
```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/quality_svm_fw_10fold_6pDef_red_mes_tpiterraintophat/",kk = 1:10,endround = 6,yrange = c(0.75,0.90),geheim = "cv_quality",error="cv_qualityerror")
predict_radial_newlegend_full(modeldata=ST_mesored,dependent = "Def_red_mes",predictors = c("TPI_i0m_o80m_10m","slope_DTM_50m_avg_ws3","sindex_vr1500_hr1500_t175","longc_ws11"),legend = ,mesolegend_gen1,doreturn=F)

print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_quality_5p_Def_red_mes_terraincols/",kk = 1:10,endround = 5,yrange = c(0.75,0.9),geheim = "cv_quality",error="cv_qualityerror")
predict_radial_newlegend_full_naomit(modeldata=NT_mesored,dependent = "Def_red_mes",predictors =c("Slope_degree_10m","TPI_i0m_o90m_10m","crosc_NT_ws70m","profc_NT_ws110m")  ,legend =mesolegend_gen1,doreturn=F)

```


##Macro scale GL2
### Geomorphons- Q

```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/quality_svm_fw_10fold_2pEZ_class_allgeoms//",kk = 1:10,endround = 2,yrange = c(0.55,0.75),geheim = "cv_quality",error="cv_qualityerror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_quality_5p_EZ_class_geomcols/",kk = 1:10,endround = 5,yrange = c(0.55,0.75),geheim = "cv_quality",error="cv_qualityerror")
predict_radial_newlegend_full(modeldata=NT_ezclass,dependent = "EZ_class",predictors =  "geom_NT_50m_avg_L300m_10deg",legend = makrolegend_gen2,doreturn=F)
predict_radial_newlegend_full(modeldata=NT_ezclass,dependent = "EZ_class",predictors =  c("geom_NT_50m_avg_L300m_10deg","geom_NT_50m_avg_L1500m_4deg","geom_NT_50m_avg_L500m_10deg"),legend = makrolegend_gen2,doreturn=F)

```

### Terrain parameters- Q
```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/quality_svm_fw_10fold_2pEZ_class_mes_tpiterraintophat/",kk = 1:10,endround = 2,yrange = c(0.55,0.75),geheim = "cv_quality",error="cv_qualityerror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_quality_5p_EZ_class_terraincols//",kk = 1:10,endround = 5,yrange = c(0.55,0.75),geheim = "cv_quality",error="cv_qualityerror")
predict_radial_newlegend_full_naomit(modeldata=NT_ezclass,dependent = "EZ_class",predictors =c("TPI_i0m_o200m_10m","profc_NT_50m_avg_ws750m","slope_NT_50m_avg_ws750m","crosc_NT_ws70m"),legend = makrolegend_gen2,doreturn=F)

```

##Meso scale GL2
### Geomorphons- Q

```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/quality_svm_fw_10fold_2pEZ_class_mes_allgeoms/",kk = 1:10,endround = 2,yrange = c(0.55,0.65),geheim = "cv_quality",error="cv_qualityerror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_quality_5p_EZ_class_mes_geomcols/",kk = 1:10,endround = 5,yrange = c(0.55,0.65),geheim = "cv_quality",error="cv_qualityerror")
predict_radial_newlegend_full_naomit(modeldata=NT_ezclassmes,dependent = "EZ_class_mes",predictors ="geom_NT_L500m_12deg",legend = mesolegend_gen2,doreturn=F)

predict_radial_newlegend_full_naomit(modeldata=NT_ezclassmes,dependent = "EZ_class_mes",predictors =c("geom_NT_L500m_12deg","geom_NT_50m_avg_L1400m_10deg","geom_NT_L400m_4deg","geom_NT_50m_avg_L1500m_1deg"),legend = mesolegend_gen2,doreturn=F)

```

### Terrain parameters- Q
```{r, echo=FALSE}
print("SOUTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/quality_svm_fw_10fold_2pEZ_class_mes_tpiterraintophat/",kk = 1:10,endround = 2,yrange = c(0.3,0.70),geheim = "cv_quality",error="cv_qualityerror")
print("NORTH TYROL")
evaluateforwardCV_anyerror("/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV_NORDTIROL/svm_fw_quality_5p_EZ_class_mes_terraincols//",kk = 1:10,endround = 5,yrange = c(0.3,0.7),geheim = "cv_quality",error="cv_qualityerror")
predict_radial_newlegend_full_naomit(modeldata=NT_ezclassmes,dependent = "EZ_class_mes",predictors =c("TPI_i50m_o100m_10m","Slope_degree_10m","profc_NT_ws150m","maxic_NT_50m_avg_ws950m"),legend = mesolegend_gen2,doreturn=F)

```
