---
title: "wrongrightanalyses"
author: "fabian gruber"
date: "01/10/2017"
output: html_document
---
To investigate whether there are some differences regarding the terrain parameters of the points that were always classified correctly, and those never, a svm-based classififcation scheme similar to that applied to the topographic positions was used to seperate these two classes of points.

At macro scale and generalisation level 1 and 2 the results are:
```{r,include=FALSE}
setwd("/home/fabs/Data/paper1_lenny/")
source("/home/fabs/Data/paper1_lenny/fabians_and_rossiters_functions.R")
load("/home/fabs/Data/paper1_lenny/mesomakrolegends.RData")
```

```{r}
evaluateforwardCV(mypath = "/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/wrongrighc_MGL1_terraintpitophat",kk = 1:10,endround = 3,type = "svm",yrange = c(0,0.6) )
```

```{r}
evaluateforwardCV(mypath = "/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/wrongrighc_MGL2_terraintpitophat",kk = 1:10,endround = 3,type = "svm",yrange = c(0,0.6) )
```

and at meso scale

```{r}
evaluateforwardCV(mypath = "/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/wrongrighc_mGL1_terraintpitophat",kk = 1:10,endround = 3,type = "svm",yrange = c(0,0.6) )
```

```{r}
evaluateforwardCV(mypath = "/home/fabs/Data/paper1_lenny/neu_unzugeordnet/FWCV/wrongrighc_mGL2_terraintpitophat",kk = 1:10,endround = 3,type = "svm",yrange = c(0,0.6) )
```


SO, the interesting terrain parameters seem to be:   
at macro GL1:  quite some improvement 
hillheight\_vr1500\_hr1000\_t125    
Texture    
crosc\_DTM\_50m\_avg\_ws5    
 TPI\_i0m\_o400m\_10m    
 
at macro GL2: hardly improvement     
TPI\_i0m\_o900m    
minic\_ws15    
crosc\_ws11    
hillheight\_vr1500\_hr1500\_t200    

at mesot GL1: quite some improvement  
slope\_ws7   
General\_Curvature     
TPI\_i0m\_o120m\_10m    

at meso GL2: no improvement   
Topographic\_Wetness\_Index  

## So, are the macro scale TPs wrong because the surveyor was more concetrated on  meso scale? 
```{r,include =F}
load("/home/fabs/Data/paper1_lenny/datawithpreds.RData")
MGL1 <- datawithpreds[!(is.na(datawithpreds$c_MGL1)),]
MGL2 <- datawithpreds[!(is.na(datawithpreds$c_MGL2)),]
mGL1 <- datawithpreds[!(is.na(datawithpreds$c_mGL1)),]
mGL2 <- datawithpreds[!(is.na(datawithpreds$c_mGL2)),]
n0 = nrow(MGL1[MGL1$c_MGL1== 0,])  #454
n6 = nrow(MGL1[MGL1$c_MGL1== 6,])  #398



importantcols <- names(datawithpreds)[c(1,55:110)]
allright_MGL1 <- datawithpreds[datawithpreds$c_MGL1 %in% c(6),importantcols]
allright_MGL1 <- merge(allright_MGL1,makrolegend_gen1,by="Def_red_mak")
allright_MGL1 <- merge(allright_MGL1,mesolegend_gen1,by="Def_red_mes")


allwrong_MGL1 <-  datawithpreds[datawithpreds$c_MGL1 %in% c(0),importantcols]
allwrong_MGL1 <- merge(allwrong_MGL1,makrolegend_gen1,by="Def_red_mak")
allwrong_MGL1$predicted <- apply(allwrong_MGL1[,c("p_fz_MGL1","p_dk_MGL1","p_wd_MGL1","p_gm_MGL1","p_tp_MGL1","p_tn_MGL1")],1,FUN=Modus)
allwrong_MGL1_withmeso<- merge(allwrong_MGL1,mesolegend_gen1,by="Def_red_mes")

allright_mGL1 <- datawithpreds[datawithpreds$c_mGL1 %in% c(6),importantcols]
allright_mGL1 <- merge(allright_mGL1,mesolegend_gen1,by="Def_red_mes")
allwrong_mGL1 <-  datawithpreds[datawithpreds$c_mGL1 %in% c(0),importantcols]
allwrong_mGL1 <- merge(allwrong_mGL1,mesolegend_gen1,by="Def_red_mes")
allwrong_mGL1$predicted <- apply(allwrong_mGL1[,c("p_fz_mGL1","p_dk_mGL1","p_wd_mGL1","p_gm_mGL1","p_tp_mGL1","p_tn_mGL1")],1,FUN=Modus)


#MGL1_tn <- merge(x=MGL1,y=makroreddata[c("AufID","hillheight_vr1500_hr1000_t125","Texture","crosc_DTM_50m_avg_ws5","TPI_i0m_o400m_10m","Normalized_Height","TPI_i0m_o250m_10m")],by="AufID",all.x=T)
#mGL1_tn <- merge(x=mGL1,y=mesoreddata[c("AufID","slope_ws7","General_Curvature","TPI_i0m_o120m_10m")],by="AufID",all.x=T)
#MGL2_tn <- merge(x=MGL2,y=makrodata[c("AufID","TPI_i0m_o900m","minic_ws15","crosc_ws11","hillheight_vr1500_hr1500_t200")],by="AufID",all.x=T)
#mGL2_tn <- merge(x=mGL2,y=mesodata[c("AufID","Topographic_Wetness_Index")],by="AufID",all.x=T)

```
  
  At Macro scale (GL1), 398 points (25\%) are always classified correctly while 454 (28\%) are always misclassified.
  At Meso scale (GL1), 499 (35\%) points are always classified correctly while 454 (32\%) are always misclassified.

The meso scale (as seen by surveyor) of the survey points that are always classified right at macro scale
```{r}
par(mfcol=c(1,2))
plot(datawithpreds[datawithpreds$c_MGL1== 6,"Def_red_mes"],las=2, main="All CORRECT",ylim=c(0,160))
plot(datawithpreds[datawithpreds$c_MGL1== 0,"Def_red_mes"],las=2,main="NEVER CORRECT",ylim=c(0,160))
```
The difference does not seem very significant, resembles more or less the overall distribution of landforms.  
Are the wrongly classified points more similar to the meso scale? lets compare confusion table of Macro and Meso:  
```{r}
print("Analysis of the points that are always misclassified")
print("MAKRORED (predicted) VS. MAKRORED (surveyor)")
table(allwrong_MGL1$predicted,allwrong_MGL1$makrogeneralized1)
print("MAKRORED (surveyed) VS. MESORED (surveyor)")
table(allwrong_MGL1$mesogeneralized1,allwrong_MGL1$makrogeneralized1)
```
  
91 of the points always misclassified have the same topographic position at meso and macro scale. 
How does this compare to those points always classified right, and overall?
```{r}
print("MAKRORED (surveyed) VS. MESORED (surveyor)")
table(allright_MGL1$mesogeneralized1,allright_MGL1$makrogeneralized1)

```
   
Here 170 points have the same topographic position at meso and macro scale, though almost always BS
------------------------
lets check what happens when the predictions for meso scale based on terrain parameters is compared to Def\_red\_mak
```{r}
print("MAKRORED (modeled) VS. MAKRORED (surveyed)")
table(allwrong_MGL1$p_tn_MGL1,allwrong_MGL1$makrogeneralized1)
```




